Conservation decision-making under long transients

### 2019-08-09 slides/boettiger.Rmd
arima example

---
background-image: linear-gradient(to right, rgba(150, 150, 150, .1), rgba(150, 150, 150, .4)), url(img/royalsociety/pensive-polarbear.jpg)
background-size: 120%
class: center, top, inverse

@@

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .6), rgba(50, 50, 50, .9)), url(img/royalsociety/whale-shark.jpg)
background-position: center
background-size: 120%
class: center, top, inverse

@@

@@

# A look at the model

@@

```{r fig.height=5.5}
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, 
          N = 4e3, x0 = 0.2, N = 1e4)
theory(p) %>%
  ggplot(aes(x, y, col=curve)) +
  geom_line(lwd = 2)

@@

```{r echo=FALSE}
theory(p) %>%
  ggplot(aes(x, potential)) + 
  geom_line(lwd = 2, col="white")

@@

```{r echo=FALSE}
det <- det_sim(may,p) %>% mutate(reps=1) %>% filter(t < 3000)
det  %>%
  ggplot(aes(t, x)) + 
  geom_line(lwd = 2, col="white")
```
---
layout: true
background-image: linear-gradient(to right, rgba(50, 50, 50, .7), rgba(50, 50, 50, .95)), url(img/royalsociety/gentoo-penguin.jpg)
background-size: 150%
class: center, top, inverse
background-position: left

@@

@@

```{r}

@@

```{r}
data %>% ggplot(aes(t,x, group=reps)) + 
  geom_line(alpha=0.02, color = "white")
```

@@

```{r echo=FALSE}
mean <- data %>% group_by(t) %>% summarise(x = mean(x)) %>% mutate(reps = 1)
data %>% ggplot(aes(t,x, group=reps)) + 
  geom_line(alpha=0.02, color = "white") + 
  geom_line(data = mean, lwd=2, color = "white")
```

@@

```{r echo=FALSE}
data %>% 
  ggplot(aes(t,x, group=reps)) + 
  geom_line(alpha=0.02, color = "white") + 
  geom_line(data = mean, lwd = 2, color = "white") +
  geom_line(data = det, lwd = 2, color = rgb(.6, .6, 1)) 
```

@@

```{r echo=FALSE}
## det equib
# data  %>% filter(t == max(t)) %>% pull(x) %>% mean() ## ~ 1.25

@@

```{r}
passage %>% ggplot(aes(tau)) + 
  geom_histogram(binwidth = 200, fill=rgb(.9, .9, .9, .7)) + 
  geom_vline(aes(xintercept=det_tau), col="blue", lwd=2)
```

@@

```{r}
discrete_sims <- read_csv("../data/discrete-sims.csv.xz")
discrete_sims %>% filter(series %in% c("1", "2")) %>% ggplot(aes(time,state)) + geom_line(col="white", lwd=1.5) + facet_wrap(~ series)
```

@@

```{r fig.width=12.5, fig.height=7}
label <- c("no switch", "switch", "no ghost")

>>>>

---
name: polarbear
background-image: linear-gradient(to right, rgba(150, 150, 150, .1), rgba(150, 150, 150, .4)), url(img/royalsociety/pensive-polarbear.jpg)
background-size: 120%
class: center, top, inverse

---
template: polarbear

@@

---
layout: true
background-image: linear-gradient(to right, rgba(50, 50, 50, .6), rgba(50, 50, 50, .9)), url(img/royalsociety/whale-shark.jpg)
background-position: center
background-size: 120%
class: center, top, inverse

@@

# Ghost Attractor

![](img/ghost.png)

# A Ghost Attractor

# Simple ARIMA forecast:

```{r}
library(stats)
x <- data %>% filter(reps == lows[[6]], t < 2000) %>% pull(x) %>% as.ts() 
fit <- arima(x)
y <- predict(fit, n.ahead = 1000) %>% as.data.frame()
y <- bind_rows(data.frame(pred = x, se = 0), y)
arima_forecast <- data %>% filter(reps == lows[[6]]) %>% select(t,x) %>% bind_cols(y)
```

```{r arima_forecast}
arima_forecast %>% ggplot(aes(t)) + 
  geom_line(aes(y=x), col="white") +
  geom_line(aes(y=pred), col="grey", lwd = 1) + 
  geom_ribbon(aes(y=pred, ymin=pred-se, ymax=pred+se), fill="white", alpha = 0.5)

@@

# A look at a candidate model

@@

```{r theory_f, fig.height=5.5}
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, 
          N = 4e3, x0 = 0.2, N = 1e4)
theory(p) %>%
  ggplot(aes(x, y, col=curve)) +
  geom_line(lwd = 2)

@@

```{r theory_U}
theory(p) %>%
  ggplot(aes(x, potential)) + 
  geom_line(lwd = 2, col="white")

@@

```{r det}
det <- det_sim(may,p) %>% mutate(reps=1) %>% filter(t < 3000)
det  %>%
  ggplot(aes(t, x)) + 
  geom_line(lwd = 2, col="white")
```
---
layout: true
background-image: linear-gradient(to right, rgba(50, 50, 50, .7), rgba(50, 50, 50, .95)), url(img/royalsociety/gentoo-penguin.jpg)
background-size: 150%
class: center, top, inverse
background-position: left

@@

```{r stoch1}
data %>% filter(reps == lows[[6]]) %>%
  ggplot(aes(t, x, group=reps)) + 
  geom_line(lwd=2, col="white") + 
  ylim(0,1.6)
```

@@

```{r stoch2}

@@

```{r stoch_all}
data %>% ggplot(aes(t,x, group=reps)) + 
  geom_line(alpha=0.02, color = "white")
```

@@

```{r ensemble}
mean <- data %>% group_by(t) %>% summarise(x = mean(x)) %>% mutate(reps = 1)
data %>% ggplot(aes(t,x, group=reps)) + 
  geom_line(alpha=0.02, color = "white") + 
  geom_line(data = mean, lwd=2, color = "white")
```

@@

```{r wtf}
data %>% 
  ggplot(aes(t,x, group=reps)) + 
  geom_line(alpha=0.02, color = "white") + 
  geom_line(data = mean, lwd = 2, color = "white") +
  geom_line(data = det, lwd = 2, color = rgb(.6, .6, 1)) 
```

@@

```{r}
## det equib
# data  %>% filter(t == max(t)) %>% pull(x) %>% mean() ## ~ 1.25

@@

```{r fpt}
passage %>% ggplot(aes(tau)) + 
  geom_histogram(binwidth = 200, fill=rgb(.9, .9, .9, .7)) + 
  geom_vline(aes(xintercept=det_tau), col="blue", lwd=2)
```

@@

```{r disc_sims}
discrete_sims <- read_csv("../data/discrete-sims.csv.xz")
discrete_sims %>% filter(series %in% c("1", "2")) %>%
  ggplot(aes(time,state)) + geom_line(col="white", lwd=1.5) + facet_wrap(~ series)
```

@@

```{r posteriors, fig.width=12.5, fig.height=7}
label <- c("no switch", "switch", "no ghost")
